---
title: "מטלה מסכמת- עקרונות יסוד של למידת מכונה"
author: "גלעד סרוסי ונעם גיל-עדי"
format: docx
lang: he
dir: rtl

editor: visual
---

## מבוא כללי
שאלה המחקר שלנו מתייחסת לדפוסי פעילות לש משתמשים באפליקציות היכרויות. באופן ספציפי Tinder. 

את מאגר הנתונים לקחנו מתוך האתר kaggle.   של המשתמש ashleyxu98
לפיו הנתונים נאספו מהאתר https://www.swipestats.io/ באישור מתאים מבעל האתר.

מטרת עבודה זו להוות התנסות ראשונית עם נתונים הלקוחים מתוך אפליקציית היכרויות, ולבחון האם נוכל לזהות דפוסים שמוכרים היתר בתחום של חברתיים.

הסט הנתונים כולל מידע שנאסף מ-1,209 משתמשים באפליקציית טינדר, ומכיל 31 עמודות המתארות פרטים דמוגרפיים והתנהגותיים: למשל מספר פתיחות של האפליקציה (sum_app_opens) מספר ימים בהם המשתמש פעיל (no_of_days) מספר ההתכתבויות הכללי (nrOfConversations) וכדומה.















##סידור הנתונים 

```{r}
#Packages loading:
library(tidyverse)
library(tidymodels)
library(finetune) # tuning hyper parameter
library(baguette)
library(randomForest) # for rand forest 
library(xgboost) # booster
library(leaps)
library(VIM) # for KNN to deal with na 


   

   
```
 
 
 
## בחירת מנבאים
 
 
```{r}
#After tidying our dataset we can get started 
 
# Splitting 
set.seed(1234)

   
# It seems that the text in the data frame has caused troubles, so I'll omits this version for now because it creates linear dependencies (?why? IDK)

finalize_df_without_text <- finalize_df |> 
  select(-text) 
   

splits <- initial_split(finalize_df_without_text, prop = 0.7)
OBJ.train <- training(splits)
OBJ.test <- testing(splits)

# Validation set:
# due to small data set size I would choose LOO-CV method for the tuning phase 

loo_validation <- loo_cv(OBJ.train)


#Comparison test sets

loo_comp <- loo_cv(OBJ.test)



#--------Defing the measures
#since this is regression problem (our Dv is the duration of objectification gaze; chest - face = dwell_chest_minus_face_wide_DV) weֿ'll asses the model's performance using R2 and MAE. 

mset_reg <- metric_set(rsq, mae)


# Selecting the Variables - Best Subset selection 

#-------------------------------------------------------------- 
full_obj_regsubset <- regsubsets(obj_indx_DV ~ .,    data = OBJ.train)
#---------------------------------------------------------------
 
# Warning: 3  linear dependencies foundReordering variables and trying again:

# ----finding the dependencies 

 alias(lm(dwell_chest_minus_face_DV ~ ., data = OBJ.train))

# It seems that all the dependencies are due to demographic information, it makes sense. For example, someone whose Native Language is Arabic is most likely Muslim 

# for now I will continue with Best Subset selection method and see what's going on, I will consider Dimension reduction next...


# ---------the Best Subsets

full_obj_regsubset_summary<-summary(full_obj_regsubset)
# I would use Matan's code to get a cleaner look at the the results of the best subsets

reg.summary_df <- data.frame(nv = 1:9, full_obj_regsubset_summary[2:6]) |> 
  pivot_longer(cols = -nv, 
               names_to = "Index", 
               values_to = "value") |> 
  group_by(Index) |> 
  mutate(
    is_best = 
      value == ifelse(Index %in% c("rsq", "adjr2"), max(value), min(value))
  )

ggplot(reg.summary_df, aes(nv, value)) +
  facet_wrap(~Index, scales = "free", ncol = 3) +
  geom_line() +
  geom_point(aes(shape = is_best), size = 3, fill = "red") +
  scale_shape_manual("Best?", values = c(20, 23)) + 
  scale_x_continuous(breaks = 1:19, minor_breaks = NULL)

## we see that R2 increases from 0% for 1-variable model, to  25%, for 9-variables model. 

#It is no surprising that R2 increase as the predictors number increase. I would go with Adj-R2 indication that 6 predictors are the best number of predictors.


# and the predictors are: 

coef(full_obj_regsubset, id = 6)

# Meeting Expectations
# Confidence level
# Liking 
# Perceived Attractiveness 
# Age 
# Religion - Being Secular 

#----------------- Testing the Subset on test set ----------- 

# Using matan function: 

predict.regsubsets <- function (object, newdata, id = NULL, 
                                select = c("adjr2", "cp", "bic")) {
  cl <- object$call
  cl[[1]] <- quote(stats::lm)
  cl[!names(cl) %in% c(formalArgs(stats::lm), "")] <- NULL
  lm_object <- eval.parent(cl)
  
  X_newdata <- model.matrix(terms(lm_object), newdata, 
                            contrasts.arg = object$contrasts)
  
  if (is.null(id)) {
    select <- match.arg(select)
    v <- summary(object)[[select]]
    id <- switch (select,
                  adjr2 = which.max(v),
                  cp = ,
                  bic = which.min(v)
    )
  }
  
  b <- coef(object, id = id)
  
  as.vector(X_newdata[, names(b), drop = FALSE] %*% b)
}

OBJ.test$pred_bss <- predict(full_obj_regsubset,
                             newdata = OBJ.test,
                             id =6) 

# R2 =0.26 on test set! 


# according to best subset selection the predictors are Meeting Expectations, Confidence level, Liking, Perceived Attractiveness, Age ,Religion. 

# this would be the preditors I would go with in the nexts models. 


```








```{r}



# -------- Random Forest ---

# Defining the specs 


 
```
