---
title: "מטלה מסכמת- עקרונות יסוד של למידת מכונה"
author: "גלעד סרוסי ונעם גיל-עדי"
format: docx
lang: he
dir: rtl

editor: visual
---

## מבוא כללי
שאלה המחקר שלנו מתייחסת לדפוסי פעילות לש משתמשים באפליקציות היכרויות. באופן ספציפי Tinder. 

את מאגר הנתונים לקחנו מתוך האתר kaggle.   של המשתמש ashleyxu98
לפיו הנתונים נאספו מהאתר https://www.swipestats.io/ באישור מתאים מבעל האתר.

מטרת עבודה זו להוות התנסות ראשונית עם נתונים הלקוחים מתוך אפליקציית היכרויות, ולבחון האם נוכל לזהות דפוסים התנהגותיים מתוך הנתונים.

הסט הנתונים כולל מידע שנאסף מ-1,209 משתמשים באפליקציית טינדר, ומכיל 31 עמודות המתארות פרטים דמוגרפיים והתנהגותיים: למשל מספר פתיחות של האפליקציה (sum_app_opens) מספר ימים בהם המשתמש פעיל (no_of_days) מספר ההתכתבויות הכללי (nrOfConversations) וכדומה.

עבודה זו תבחן האם הנטיה לעשות למישהו גוסטינג( ניתוק קשר ללא התראה מוקדמת) יכולה להיות מנובאת מהתנהגויות אחרות בפלטפורמה, או נתונים דמוגרפים כלשהן.













##Pre-Processing 

```{r}
#Packages loading:
library(tidyverse)
library(tidymodels)
library(finetune) # tuning hyper parameter
library(randomForest) # for rand forest 
library(xgboost) # booster
library(leaps)
library(vip) 

Tinder_df <- read.csv("./data/tinder-data/Tinder_Data_v3_Clean_Edition.csv")
#this data frame is containsing 1209 users and properties that define this user: numer of matchs, the median length of a conversation, number of swiping 'like' etc.

#First and foremost, we would get read of bad instances in our dataset. specifically those user whose hasn't been active at all 





Tinder_filtered <- Tinder_df  |> 
  
   
  #Omit users that didn't open the app at all, and those how haven't engaged in it 
  
  filter(sum_app_opens > 0 & swipe_likes >0 & swipe_passes > 0)  |> 
  
  # Or those users who never engaged in a conversation
  
  filter(medianConversationLength > 0)  |> 
  
  # Factor conversions

  mutate(instagram = as.factor(instagram),
         spotify = as.factor(spotify),
         gender= as.factor(gender)
         ) |> 
  
  #Creating an heterosexual column for easier interpretation. 
  
    mutate( hetero_sx =  as.factor(ifelse(
   (gender == "M" & interestedIn == "F") | (gender == "F" & interestedIn == "M"),
   1,
   0
  ))) |> 
  select(-c(interestedIn))  |> 
  
  #------ Dealing with weird outliers 

  # Some value in  'ageFilterMax' are set to 1000 (???), which is clearly unrealistic.
  # Based on my (unfortunate) domain knowledge valid age value should ranges from 1 to 100. 
  # We'll correct these by replacing 1000 with the next-highest valid age. (assuming this
  # is an arbitrary error [ while parsing the data maybe] rather than a invalid user. and
  #review of other user attributes of those instances supports this assumption)
  
  mutate(ageFilterMax = replace(
    ageFilterMax,
    ageFilterMax == max(ageFilterMax, na.rm = TRUE),
    sort(unique(ageFilterMax), decreasing = TRUE)[2]
  )) |> 
  
  #The same goes for our outcome variable 'nrOfGhostingsAfterInitialMessage'
  
    mutate(nrOfGhostingsAfterInitialMessage = replace(
    nrOfGhostingsAfterInitialMessage,
    nrOfGhostingsAfterInitialMessage == max(nrOfGhostingsAfterInitialMessage,
                                            na.rm = TRUE),
    sort(unique(nrOfGhostingsAfterInitialMessage),
         decreasing = TRUE)[2]
  ))


# there's still some outliers in our outcome variable. 
hist(Tinder_filtered$nrOfGhostingsAfterInitialMessage)

#lets try the Z score outliers detections - above 3 Standard deviation

z_score_no_ghst<- scale(Tinder_filtered$nrOfGhostingsAfterInitialMessage)

outliers <- Tinder_filtered$nrOfGhostingsAfterInitialMessage[abs(z_score_no_ghst) > 3]

length(outliers)

# only 23 instances are above/below 3 standard deviation from the average mean, I would regard those as outliers and therefore remove them 

Tinder_filtered <- Tinder_filtered |> 
  mutate(z_ghost = z_score_no_ghst) |>
  filter(abs(z_ghost) <= 3) |> 
  select(-z_ghost)
  
  

# Since my models of Interest are not an OLS/GKM ones, and given that I do want to interpret the results of such modeling, I would not conduct any dimension reduction method. 
# My models of choice would be Boosting and Random Forest. 

```

## Modeling

```{r}
# Data Splitting (70%):
set.seed(130597)
splits <- initial_split(Tinder_filtered,
                        prop = 0.7)
Tinder.train <- training(splits)
Tinder.test <- testing(splits)

# Cross Validation and Comparisons sets

# Bootstraps Spliting
Tinder_validation_sets <- bootstraps(
  Tinder.train,
  times = 50,
  strata = NULL,
  apparent = F
)

Tinder_comparison_sets <- bootstraps(
  Tinder.test,
  times = 50,
  strata = NULL,
  apparent = F
)

#the predictions would be evaluated using R2 and MAE

mset_reg <- metric_set(rsq, mae)

# ---------------- Recipe-------------------

# let's define the models R

# Predicting number of ghosting after initial message:

rec <- recipe(nrOfGhostingsAfterInitialMessage ~ .,
              data = Tinder_filtered) |> 
   #for our purposes we would omit some demographics that are not of high intrests for us,   since we would like to examine patterns across nationalities and times.
  
   #after visually inspecting the data frame I can say the the 'education' is not valid. I  found quite a few professionals with no education (physician fro example) 
  
  #I will omit jobTitle because I it seems that the textual analysis tool would be more sufficient in capturing the complexities of this variable  
  step_rm(country,
          cityName,
          createDate,
          education,
          jobTitle,
          X_id,
          birthDate) |> 
  
  
  #dealing with factors 
  step_dummy(spotify,
             gender,
             instagram,
             hetero_sx) 
  
  

# -------------------------  Spec- Random Forest ------------------

rf_spec <- rand_forest(
  mode = "regression",
  engine = "randomForest",
  
  #we will tune these hyper-parameters
  
  mtry = tune(),
  trees = tune(),
  min_n = 5
)

rf_wf <- workflow(preprocessor = rec, spec = rf_spec)


rf_grid <-  grid_regular(
  
  #Considering to computation time I would reduce the max number of predictors to 10 
  mtry(range = c(1, 10)),
  trees(range = c(100, 1000)),
  levels = 5
)

rf_tuner <- tune_grid(rf_wf,
                      resamples = Tinder_validation_sets,
                      grid = rf_grid,
                      metrics = mset_reg)
#started running - 13:14

```
















 
 
## בחירת מנבאים
 
 
```{r}
#After tidying our dataset we can get started 
 
# Splitting 
set.seed(1234)

   
# It seems that the text in the data frame has caused troubles, so I'll omits this version for now because it creates linear dependencies (?why? IDK)

finalize_df_without_text <- finalize_df |> 
  select(-text) 
   

splits <- initial_split(finalize_df_without_text, prop = 0.7)
OBJ.train <- training(splits)
OBJ.test <- testing(splits)

# Validation set:
# due to small data set size I would choose LOO-CV method for the tuning phase 

loo_validation <- loo_cv(OBJ.train)


#Comparison test sets

loo_comp <- loo_cv(OBJ.test)



#--------Defing the measures
#since this is regression problem (our Dv is the duration of objectification gaze; chest - face = dwell_chest_minus_face_wide_DV) weֿ'll asses the model's performance using R2 and MAE. 

mset_reg <- metric_set(rsq, mae)


# Selecting the Variables - Best Subset selection 

#-------------------------------------------------------------- 
full_obj_regsubset <- regsubsets(obj_indx_DV ~ .,    data = OBJ.train)
#---------------------------------------------------------------
 
# Warning: 3  linear dependencies foundReordering variables and trying again:

# ----finding the dependencies 

 alias(lm(dwell_chest_minus_face_DV ~ ., data = OBJ.train))

# It seems that all the dependencies are due to demographic information, it makes sense. For example, someone whose Native Language is Arabic is most likely Muslim 

# for now I will continue with Best Subset selection method and see what's going on, I will consider Dimension reduction next...


# ---------the Best Subsets

full_obj_regsubset_summary<-summary(full_obj_regsubset)
# I would use Matan's code to get a cleaner look at the the results of the best subsets

reg.summary_df <- data.frame(nv = 1:9, full_obj_regsubset_summary[2:6]) |> 
  pivot_longer(cols = -nv, 
               names_to = "Index", 
               values_to = "value") |> 
  group_by(Index) |> 
  mutate(
    is_best = 
      value == ifelse(Index %in% c("rsq", "adjr2"), max(value), min(value))
  )

ggplot(reg.summary_df, aes(nv, value)) +
  facet_wrap(~Index, scales = "free", ncol = 3) +
  geom_line() +
  geom_point(aes(shape = is_best), size = 3, fill = "red") +
  scale_shape_manual("Best?", values = c(20, 23)) + 
  scale_x_continuous(breaks = 1:19, minor_breaks = NULL)

## we see that R2 increases from 0% for 1-variable model, to  25%, for 9-variables model. 

#It is no surprising that R2 increase as the predictors number increase. I would go with Adj-R2 indication that 6 predictors are the best number of predictors.


# and the predictors are: 

coef(full_obj_regsubset, id = 6)

# Meeting Expectations
# Confidence level
# Liking 
# Perceived Attractiveness 
# Age 
# Religion - Being Secular 

#----------------- Testing the Subset on test set ----------- 

# Using matan function: 

predict.regsubsets <- function (object, newdata, id = NULL, 
                                select = c("adjr2", "cp", "bic")) {
  cl <- object$call
  cl[[1]] <- quote(stats::lm)
  cl[!names(cl) %in% c(formalArgs(stats::lm), "")] <- NULL
  lm_object <- eval.parent(cl)
  
  X_newdata <- model.matrix(terms(lm_object), newdata, 
                            contrasts.arg = object$contrasts)
  
  if (is.null(id)) {
    select <- match.arg(select)
    v <- summary(object)[[select]]
    id <- switch (select,
                  adjr2 = which.max(v),
                  cp = ,
                  bic = which.min(v)
    )
  }
  
  b <- coef(object, id = id)
  
  as.vector(X_newdata[, names(b), drop = FALSE] %*% b)
}

OBJ.test$pred_bss <- predict(full_obj_regsubset,
                             newdata = OBJ.test,
                             id =6) 

# R2 =0.26 on test set! 


# according to best subset selection the predictors are Meeting Expectations, Confidence level, Liking, Perceived Attractiveness, Age ,Religion. 

# this would be the preditors I would go with in the nexts models. 


```








```{r}



# -------- Random Forest ---

# Defining the specs 


 
```
